Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-03-22 src/docs_paper/paper.Rmd
Add Naomi outputs figure to paper

Using one `TMB` C++ user-template (available in the appendix), we fit the simplified Naomi model (Section \ref{sec:naomi}) to data from Malawi using four inferential approaches.
These were:
1. `TMB`: EB combined with a Gaussian approximation via `TMB`,
2. `aghq`: AGHQ combined with a Gaussian approximation via `aghq`,
3. `adam`: AGHQ combined with a Laplace approximation by extending `aghq`, and
4. `NUTS`: the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using Stan [@carpenter2017stan] via the `tmbstan` package [@monnahan2018no].
In this instance, the dimension of the latent field $N = 491$ and the dimension of the hyperparameters $m = 24$.
Settings used for each inferential method are provided in Table \ref{tab:inference-methods}.
For the deterministic methods, following inference we simulated hyperparameter and latent field samples.
For all methods, we simulated age-sex-district specific HIV prevalence, ART coverage and HIV incidence from the latent field and hyperparameter posteriors.
The \textsc{R} [@r] code used to produce all results we describe below is available at `github.com/athowes/elgm-inf`.
We used `orderly` [@orderly] for reproducible research, `ggplot2` for data visualisation [@wickham2016ggplot2] and `rticles` [@allaire2022rticles] for reporting via `rmarkdown` [@allaire2022rmarkdown].

>>>>

Using one `TMB` C++ user-template (available in the appendix), we fit the simplified Naomi model (Section \ref{sec:naomi}) to data from Malawi using four inferential approaches.
These were:
1. `TMB`: EB combined with a Gaussian approximation via `TMB`,
2. `aghq`: AGHQ combined with a Gaussian approximation via `aghq`,
3. `adam`: AGHQ combined with a Laplace approximation by extending `aghq`, and
4. `NUTS`: the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using Stan [@carpenter2017stan] via the `tmbstan` package [@monnahan2018no].
In this instance, the dimension of the latent field $N = 491$ and the dimension of the hyperparameters $m = 24$.
Settings used for each inferential method are provided in Table \ref{tab:inference-methods}.
For the deterministic methods, following inference we simulated hyperparameter and latent field samples.
For all methods, we simulated age-sex-district specific HIV prevalence, ART coverage and HIV incidence from the latent field and hyperparameter posteriors.
<!-- Note: eventually this figure should be generated using the algorithm proposed in the paper -->
Example model outputs from `TMB` are illustrated in Figure \ref{fig:naomi-results}.
The \textsc{R} [@r] code used to produce all results we describe below is available at `github.com/athowes/elgm-inf`.
We used `orderly` [@orderly] for reproducible research, `ggplot2` for data visualisation [@wickham2016ggplot2] and `rticles` [@allaire2022rticles] for reporting via `rmarkdown` [@allaire2022rmarkdown].

```{r naomi-results, fig.cap="District-level model outputs for adults aged 15-49. Inference conducted with \\texttt{TMB}."}
knitr::include_graphics("depends/naomi_results.png")
```
